---
title: "Visualizing some socio-economic Indicators"
output: github_document
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
```


Visualizing socio-economic indicators is crucial for facilitating comprehensive understanding and informed decision-making. Through visual representation, complex data sets become more accessible and digestible, enabling stakeholders, policymakers, and researchers to identify spatial patterns, disparities, and trends across regions. Visualization enhances communication by providing compelling insights into the status and distribution of key indicators, thereby guiding resource allocation, policy formulation, and targeted interventions aimed at addressing socio-economic challenges and promoting sustainable development in affected areas. Below are examples of some indicators for Africa. 

## Africa Infrastructure Development Index

The development of infrastructure in Africa is vital for economic growth and human development, and to reduce poverty while achieving the Sustainable Development Goals (SDGs).

```{r echo=FALSE, size='tiny', setOptions}
library(tidyverse)
library(readxl)
library(highcharter)
library(webshot2)

## get the column names
aidiColumnNames <- as.character(
  read_excel("data/Africa Infrastructure Development Index AIDI Index.xlsx",
             sheet = "AIDI",
             n_max = 1,
             range = "R7C1:R7C21",
             col_names = FALSE)
)

## read the data
aidi.2022 <- read_excel("data/Africa Infrastructure Development Index AIDI Index.xlsx",
                        sheet = "AIDI",
                        range = cell_cols("A:U"),
                        col_names = aidiColumnNames) %>%
  slice(7:n()) %>%
  rename(Y2022=`2022`) |> 
  select(Country,ISO,Y2022) |> 
  mutate(Y2022=as.numeric(Y2022))

hcmap(
  map="custom/africa", #world-robinson-lowres",
  data = aidi.2022,
  name = "Gross national income per capita",
  value = "Y2022",
  borderWidth = 0,
  nullColor = "#d3d3d3",
  joinBy = c("iso-a2", "ISO")
) |>
  hc_colorAxis(
    stops = color_stops(colors = viridisLite::viridis(10, begin = 0, direction = -1))
  )

```  

